\section{Benchmark, Metrics, and Methodology}
\label{sec:methodology}

% =============================================================================
\subsection{Benchmark}
\label{sec:methodology:benchmark}

\input{figures/pipeline}
Fig.~\ref{fig:pipeline} sketches the full measurement pipeline.

We selected 15 cipher primitives spanning six architecture families:
four 4-bit S-boxes (PRESENT, GIFT, PRINCE, PRINCE$^{-1}$); three
substitution round functions (GIFT \texttt{subcells}, GIFT round,
PRESENT round); one permutation primitive (PRINCE $M'$); two SIMON
round functions (SIMON-32, SIMON-64); two Keccak-$\chi$ widths
(5-bit, 64-row); and three ARX primitives (Speck-32, SpecKey,
MARX-2). Input width ranges from 4 to 1280 bits. FPGA-oriented
AOIG/MIG metrics are included in the artifact for context, but
the fault-analysis claims below use the BLIF-level campaigns.

We analyze three logical representations, all derived from the same raw
cipher BLIF. \emph{LUT/AOIG} is the raw BLIF emitted by Yosys 0.9 from
the cipher's behavioral description, dominated by LUT-style truth-table
primitives. \emph{AIG} is a decomposed 2-input AND-inverter graph, used as a
comparable small-gate granularity control.
\emph{MIG} is a strict 3-input majority-inverter network produced with
the mockturtle logic-synthesis library~\cite{soeken2018mockturtle}. The
exact passes for the AIG and MIG flows are given in
\S\ref{sec:methodology:recipes}; the raw BLIFs and the synthesis driver
are in the artifact.

% =============================================================================
\subsection{Synthesis recipes}
\label{sec:methodology:recipes}

Because our central claim is that fault metrics depend on the gate-level
representation, the exact transformation from the common source BLIF to
each representation is part of the methodology. All three start from the
identical Yosys-emitted truth-table BLIF.

\textit{AIG.} We decompose the source BLIF into a 2-input AND-inverter
graph with Yosys and ABC, using the script
\texttt{read\_blif; hierarchy -auto-top; flatten; proc; techmap; opt;
abc -g AND; opt\_clean; write\_blif}. The \texttt{abc -g AND} step maps
all logic onto 2-input \textsc{and} nodes with inverter edges; no
optimization beyond \texttt{opt}/\texttt{opt\_clean} is applied. This
control exists only to provide a comparable small-gate fault-site
population for comparison with the MIG.

\textit{MIG.} We read the source BLIF into a $k$-LUT network and convert
it to an MIG by NPN node resynthesis
(\texttt{node\_resynthesis} with \texttt{mig\_npn\_resynthesis}). We then
apply a fixed DAC'19-style majority optimization recipe implemented with
stock mockturtle passes~\cite{amaru2019synth}: algebraic depth rewriting,
MIG resubstitution, cut rewriting with MIG NPN resynthesis, and
refactoring. In the artifact, this recipe is selected with
\texttt{--mode=area --mig-flow=dac19\_compat}; the option is used only
to reproduce the mockturtle flow. The resulting netlists are strict
3-input majority-inverter graphs.

% =============================================================================
\subsection{Metrics}
\label{sec:methodology:metrics}

We measure \emph{fault observability}: after flipping one gate-output
bit, does any primary output change, and if so, how often and by how
many bits? This is not a full key-recovery metric. It is a gate-level
description of how injected faults reach the circuit outputs.

Let $C$ have primary inputs $I$, primary outputs $O$, and internal
signals $G(C)$. Let $\mathcal{P}$ be the test-vector set (exhaustive
when $|I| \le 20$, otherwise $10{,}000$ uniform random vectors with
fixed seed). For each fault site $g \in G(C)$ and each vector
$P \in \mathcal{P}$, let $\text{out}(P)$ denote the fault-free primary
outputs and $\text{out}_g(P)$ the primary outputs when $g$ is subject
to a single \bitflip{}. We report three metrics.

\textit{Fault coverage} \FCpct{} asks how many gate-output sites are
ever visible at the primary outputs. A site is detectable if at least
one tested vector makes the faulty output differ from the fault-free
output:
$|\{g : \exists P,\ \text{out}_g(P) \ne \text{out}(P)\}| / |G(C)|$.

\textit{Average per-vector detection probability} \AvgDP{} asks how
often a detectable site is visible. For a site $g$, $\text{dp}(g)$ is
the fraction of tested vectors on which flipping $g$ changes the
primary output. \AvgDP{} averages this value across detectable sites:
$\AvgDP(C) = \frac{1}{|\{g~\text{detectable}\}|} \sum_g \text{dp}(g)$,
where $\text{dp}(g) = |\{P : \text{out}_g(P) \ne \text{out}(P)\}| / |\mathcal{P}|$.
For example, if a fault changes the output on 8 of 16 exhaustive input
vectors, then $\text{dp}(g)=0.5$.

\textit{Average breadth} \AvgBW{} asks how large the visible corruption
is. For every event where the faulty output differs from the correct
output, we count the primary-output Hamming distance. \AvgBW{} is the
mean of those distances over all detecting events.

These metrics vary independently. A circuit can have higher \FCpct{}
than another while having lower \AvgDP{}: more fault sites are
theoretically observable, but each is observed on a smaller share of
input space.

For the granularity-controlled analysis, we compute each metric over two
fault-site populations. The \emph{all-site} population includes every
gate-output site in the representation. This is the common campaign
design, but it is representation-sensitive because decomposing one
Boolean function into many small gates changes both the number and
location of sites being averaged. The \emph{target-layer} population
includes only gates that directly drive primary outputs. This is not a
complete physical fault model, but it is a realizable combinational DFA
target layer and removes the interior-node mix introduced by different
decompositions. Full definitions are in the artifact's
\texttt{paper/metrics.md}.

% =============================================================================
\subsection{Fault model and simulator}
\label{sec:methodology:simulator}

We adopt a single-fault model: the adversary injects one
\bitflip{} at one gate-output wire of the combinational netlist per
evaluation and observes the resulting primary outputs. We do not
model multi-bit faults, transistor-level effects, glitch injection,
delay faults, or end-to-end key-recovery attacks; these are
out of scope.

Our simulator parses BLIF, builds per-gate truth-table lookups, and
evaluates the netlist on all $|\mathcal{P}|$ vectors as a single
vectorized \texttt{numpy.uint8} array. For each gate $g$, the
fault-free signal value $v_g(P)$ is computed once; the faulty
evaluation re-runs propagation with the override
$g \mapsto v_g(P) \oplus 1$. The campaign re-runs full propagation for
each fault site across all test vectors in a vectorized batch; for
the largest circuit (\texttt{keccak\_chi\_64row}, 1602 gates,
$10{,}000$ vectors) it completes in approximately one minute on a
single core.

% =============================================================================
\subsection{Granularity-controlled assessment procedure}
\label{sec:methodology:procedure}

The assessment has three checks. First, we compute all-site \AvgDP{}
for each representation and compare the same MIG netlists against both
the LUT/AOIG baseline and the decomposed-AIG baseline. Second, we
measure the Spearman rank association between all-site \AvgDP{} and
decomposition granularity (fault sites per primary output). Third, we
repeat the campaign on the target-layer population only. These checks
allow us to separate representation-dependent all-site behavior from
behavior that remains stable under controlled fault-site populations.
Results are reported in \S\ref{sec:results}.

% =============================================================================
\subsection{Mechanism: how masking arises}
\label{sec:methodology:mechanism}

The LUT-to-MIG \AvgDP{} change in \S\ref{sec:results:granularity}
has a concrete gate-level mechanism, but the mechanism is a site-mix
effect, not evidence that majority logic is intrinsically more
fault resistant. A \bitflip{} at the output of
gate $g$ is, by definition, observable at $g$ itself because the fault
and the output are the same wire. The question is whether the flipped
value reaches a primary output, which depends entirely on $g$'s
downstream consumers.

For a 3-input majority gate $h$ that consumes $g$ along with two
other inputs $a$ and $b$, the output of $h$ is $1$ iff at least two of
its three inputs are $1$. The vote is \emph{determined} by $a$ and
$b$ alone when $a = b$: $h$'s output is fixed at that shared value
regardless of the third input. We call this the \emph{non-controlling
pattern at $h$ relative to $g$}, in keeping with the ATPG term. When
the other two inputs disagree, $a \ne b$, the third input casts the
deciding vote, and a flip at $g$ propagates through $h$.

Under a uniform distribution over $h$'s other two inputs, the
non-controlling pattern holds with probability $\frac{1}{2}$.
A fault at $g$ that has no downstream consumer other than $h$ therefore
has $\text{dp}(g) = \frac{1}{2}$ in the limit. A LUT-style AOIG
representation often contributes one wide output-adjacent fault site
with $\text{dp}=1$, whereas MIG and AIG decompositions contribute many
interior sites whose downstream consumers can mask them. The all-site
average therefore changes when the representation changes. The central
question in \S\ref{sec:results:granularity} is whether the sign of that
change survives when the baseline is decomposed to comparable
granularity.

% =============================================================================
\subsection{Worked example}
\label{sec:methodology:trace}

We make the mechanism concrete on the \texttt{present\_sbox} MIG
netlist. Gate $g = \texttt{new\_n12}$ is a 3-input majority of
\texttt{pi1}, \texttt{pi2}, and an internal signal \texttt{new\_n11}.
$g$ has exactly one downstream consumer, $h = \texttt{new\_n15}$,
which is a 3-input majority over \texttt{new\_n10}, the complement of
$g$'s value, and \texttt{new\_n14}.
Figure~\ref{fig:masking-example} shows the structure;
Table~\ref{tab:masking-trace} enumerates the per-vector behavior.

\input{../mechanism_example/figure_masking}
\input{../mechanism_example/table_trace}

Over the $2^4 = 16$ exhaustive input vectors, the other two inputs
of $h$ agree on exactly 8 vectors. On those 8 vectors, $h$'s output is
fixed by \texttt{new\_n10} and \texttt{new\_n14}, and the flip at $g$
does not propagate. On the other 8 vectors, \texttt{new\_n10} and
\texttt{new\_n14} disagree, $h$'s output tracks $g$'s value, and the
flip propagates to a primary output. The measured $\text{dp}(g)$ is
$8/16 = 0.5$, exactly the predicted MAJ-3 per-input non-controlling
rate.

This example does not establish a representation-level security
advantage. It shows that downstream majority masking exists and is
identifiable at the gate level. The granularity-controlled
results in \S\ref{sec:results:granularity} show why this local mechanism
must be interpreted together with the distribution of fault sites created
by the synthesis flow.

% =============================================================================
\subsection{Hardware target and reproducibility}
\label{sec:methodology:fpga}

For the FPGA side data included in the artifact, we synthesized each
circuit on a Xilinx Spartan-7 \texttt{xc7s100fgga676-2}
using Vivado 2023.2 with \texttt{synth\_design -flatten\_hierarchy
rebuilt}. Each LUT1 inverter is annotated \texttt{DONT\_TOUCH = TRUE}
post-synthesis to preserve inverter visibility in the LUT histogram;
the target clock period is 10\,ns. The fault-analysis path of the
paper does not depend on FPGA tooling; the post-optimization BLIFs
are included in the artifact and the fault metrics are reproducible
from them on a stock Python 3.10 with NumPy installation.

The accompanying artifact contains the cipher BLIFs,
the synthesized netlists, the fault simulator, the table and figure
generators, and a verification script that checks the quoted summary
numbers against the raw JSON outputs.
