\section{Discussion}
\label{sec:discussion}

% =============================================================================
\subsection{What should be reported}
\label{sec:discussion:reporting}

The main lesson is methodological. All-site fault metrics are meaningful
only together with the fault-site population they average over. Reporting
\AvgDP{} without the representation granularity can make a decomposition
look like a defense or a regression depending on the chosen baseline. A
minimum report should therefore include the number of fault sites,
fault sites per primary output, whether sites are all internal gates or a
targeted layer, and the synthesis pass that created the baseline. For
cross-representation comparisons, we recommend pairing all-site metrics
with at least one controlled metric. A decomposed-AIG baseline at
comparable small-gate granularity tests whether the effect is specific
to the logic primitive rather than to decomposition size, while a
target-layer metric tests whether the output-driving layer changes when
interior nodes are excluded. In our benchmark, both controls overturn
the naive LUT-to-MIG interpretation.

% =============================================================================
\subsection{What remains useful}
\label{sec:discussion:robust}

The granularity control does not make the artifact negative. It separates
three kinds of claims. First, the LUT-to-MIG \AvgDP{} reduction is a
real property of that pair of netlists, useful if a designer specifically
cares about all internal sites in those representations. Second, the
target-layer result shows that this reduction should not be promoted to a
representation-independent fault-resistance claim. Third, the ARX
\AvgBW{} result survives the controls and is therefore a stronger
design fact.

% =============================================================================
\subsection{Limits}
\label{sec:discussion:limits}

Our limits follow from the model and sampling choices. We model one
transient \bitflip{} at one gate-output wire; stuck-at faults, delay
faults, multi-bit faults, and physical injection footprints may interact
with representation granularity differently. For large circuits we use a
fixed 10,000-vector uniform random sample, while small circuits are
exhaustive. An adversary who can choose inputs may target vectors that
maximize or minimize propagation, so worst-case input search remains a
separate attack problem.

The target-layer and architecture-level results also have bounded scope.
Output-driving gates form a clean controlled layer, not a complete
physical adversary model. They are useful because the layer exists in
every representation and avoids the interior-node population shift, but
other fixed layers could be studied. The ARX result uses three ARX
primitives and seven substitution-based primitives; its no-overlap
pattern is strong in this benchmark, but a wider set of addition-chain
and substitution designs is needed before treating the ratio as a
general law. Finally, none of the metrics directly measures key recovery:
\FCpct{}, \AvgDP{}, and \AvgBW{} describe observability and output
corruption, while the algebraic usefulness of those differences remains
cipher-specific.
